Security Metrics for the Android Ecosystem

### 2015-07-28 spsm04-thomas.tex
Abstract tweak.
Removed network operator from conclusions.

\begin{abstract}
The security of Android depends on the timely delivery of updates to fix critical vulnerabilities.
In this paper we map the complex network of players in the Android ecosystem who must collaborate to provide updates, and determine that inaction by some manufacturers and network operators means many handsets are vulnerable to critical vulnerabilities.
We define the FUM security metric to rank the performance of device manufacturers and network operators, based on their provision of updates and exposure to critical vulnerabilities.
Using a corpus of \daNumOSDevices\ devices we show that there is significant variability in the timely delivery of security updates across different device manufacturers and network operators.
This provides a comparison point for purchasers and regulators to determine which device manufacturers and network operators provide security updates and which do not.
We find that on average \daMeanInsecurityPercNominal\ of Android devices are exposed to at least one of \daNumVulnsUsed\ known critical vulnerabilities and, across the ecosystem as a whole, assign a FUM security score of \daSecurityScoreNominal\ out of 10. In our data, Nexus devices do considerably better than average with a score of \daSecScoreBestsummaryScoreNominal; \daSecScoreBestmanufacturer\ is the best manufacturer with a score of \daSecScoreBestmanufacturerScoreNominal.
%On average \daMeanOutstandingVulnerabilitiesNominal\ outstanding vulnerabilities are not fixed on any device and on average only \daUpdatednessPercNominal\ of devices run the current version of Android.
\end{abstract}

@@

\section{Conclusion}
The security of Android depends on the timely delivery of updates to fix critical vulnerabilities.
Unfortunately few devices receive prompt updates, with an overall average of \daUpdatesPerYearNominal\ updates per year, leaving devices unpatched for long periods.
We showed that the bottleneck for the delivery of updates in the Android ecosystem rests with the manufacturers and network operators, who fail to provide updates to fix critical vulnerabilities.
This arises in part because the market for Android security today is like the market for lemons: there is information asymmetry between the manufacturer, who knows whether the device is currently secure and will receive updates, and the consumer, who does not.

>>>>

\begin{abstract}
The security of Android depends on the timely delivery of updates to fix critical vulnerabilities.
In this paper we map the complex network of players in the Android ecosystem who must collaborate to provide updates, and determine that inaction by some manufacturers and network operators means many handsets are vulnerable to critical vulnerabilities.
We define the FUM security metric to rank the performance of device manufacturers and network operators, based on their provision of updates and exposure to critical vulnerabilities.
Using a corpus of \daNumOSDevices\ devices we show that there is significant variability in the timely delivery of security updates across different device manufacturers and network operators.
This provides a comparison point for purchasers and regulators to determine which device manufacturers and network operators provide security updates and which do not.
We find that on average \daMeanInsecurityPercNominal\ of Android devices are exposed to at least one of \daNumVulnsUsed\ known critical vulnerabilities and, across the ecosystem as a whole, assign a FUM security score of \daSecurityScoreNominal\ out of 10. In our data, Nexus devices do considerably better than average with a score of \daSecScoreBestsummaryScoreNominal; and \daSecScoreBestmanufacturer\ is the best manufacturer with a score of \daSecScoreBestmanufacturerScoreNominal.
%On average \daMeanOutstandingVulnerabilitiesNominal\ outstanding vulnerabilities are not fixed on any device and on average only \daUpdatednessPercNominal\ of devices run the current version of Android.
\end{abstract}

@@

\section{Conclusion}
The security of Android depends on the timely delivery of updates to fix critical vulnerabilities.
Unfortunately few devices receive prompt updates, with an overall average of \daUpdatesPerYearNominal\ updates per year, leaving devices unpatched for long periods.
We showed that the bottleneck for the delivery of updates in the Android ecosystem rests with the manufacturers, who fail to provide updates to fix critical vulnerabilities.
This arises in part because the market for Android security today is like the market for lemons: there is information asymmetry between the manufacturer, who knows whether the device is currently secure and will receive updates, and the consumer, who does not.
